Title

### 2023-05-16 main.tex
Pequeño arreglo

Following this procedure for random
angles and unitary matrices $V$, 
we plot four Pauli dynamical maps 
that can be implemented with a 1PR circuit in \fref{fig:curves-random}.
These maps where constructed with the additional condition
of passing through the identity channel.
To do that, we ensure that the vectors also satisfy
$\vec{a} + \vec{b} + \vec{c} = (e^{i \theta},0,0,0)$ with $\theta$ an arbitrary
number.
This way, when $s = 0$ in \eref{eq:vec}, the constructed state
is $(e^{i \theta},0,0,0)$, which
corresponds with the identity channel.

To fulfill this additional condition,  we restrict the first row of
$V$ to be $e^{i\theta} (|\vec{a}|, |\vec{b}|, |\vec{c}|,0)$. 
That way, 
\begin{align*}
\vec{a} + \vec{b} + \vec{c} = U (\vec{a'} + \vec{b'} + \vec{c'}) = U(|\vec{a}|, |\vec{b}|, |\vec{c}|,0)^T = (e^{i\theta},0,0,0)^T.
\end{align*}
The last step is because the first entry of $V(|\vec{a}|, |\vec{b}|, |\vec{c}|,0)^T$
is obtained by calculating the dot product of the first row of $U$ with $(|\vec{a}|, |\vec{b}|, |\vec{c}|,0)^T$, which gives
$e^{i\theta}$. 
Furthermore, the other entries have to be $0$,
since otherwise the norm of the result would be greater than
one but $V$ preserves the norm.

>>>>

Following this procedure for random
angles and unitary matrices $V$, 
we plot four Pauli dynamical maps 
that can be implemented with a 1PR circuit in \fref{fig:curves-random}.
These maps where constructed with the additional condition
of passing through the identity channel.
To do that, we ensure that the vectors also satisfy
$\vec{a} + \vec{b} + \vec{c} = (e^{i \theta},0,0,0)$ with $\theta$ an arbitrary
real number.
This way, when $s = 0$ in \eref{eq:vec}, the constructed state
is $(e^{i \theta},0,0,0)$, which
corresponds with the identity channel.

To fulfill this additional condition,  we restrict the first row of
$V$ to be $e^{i\theta} (|\vec{a}|, |\vec{b}|, |\vec{c}|,0)$. 
That way, 
\begin{align*}
\vec{a} + \vec{b} + \vec{c} = V (\vec{a'} + \vec{b'} + \vec{c'}) = V(|\vec{a}|, |\vec{b}|, |\vec{c}|,0)^T = (e^{i\theta},0,0,0)^T.
\end{align*}
The last step is because the first entry of $V(|\vec{a}|, |\vec{b}|, |\vec{c}|,0)^T$
is obtained by calculating the dot product of the first row of $V$ with $(|\vec{a}|, |\vec{b}|, |\vec{c}|,0)^T$, which gives
$e^{i\theta}$. 
Furthermore, the other entries have to be $0$,
since otherwise the norm of the result would be greater than
one but $V$ preserves the norm.
